---
title: "JEDI Audit - Data Cleaning"
author: "Shashi Ponraja"
date: "26/02/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Joondalup Cardiac Electronic  Device Implantation Audit - Data Cleaning

This set of scripts is designed to convert all the raw data collected from our audit into a neat package

1. Unify Device Information.xlsx into a single data frame / csv file

2. Categorize all equipment by device type

3. Produce a list of all devices every individual patient has had inserted

4. Create a giant data frame that has all our data in it

5. Take the compiled data and transmogrify into one epic data set

6. Give it to somebody else to sort out

7. ???

8. Profit

To Do list
Extract a list of all equipment used, and classify its device type
De-identify data


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
